Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/inverted_u.tex
Remove old \asedit commands.

\xhdr{Welfare.}
\asedit{We study the effects of competition on consumer welfare: the total reward collected by the users over time. Rather than welfare directly, we find it more lucid to consider
\emph{market regret}:
\[ \textstyle T\, \max_a \mu(a) - \sum_{t\in [T]} \mu(a_t), \]
where $a_t$ is the arm chosen by agent $t$. This is a standard performance measure in the literature on multi-armed bandits. Note that smaller regret means higher welfare.}

@@

\asedit{We assume that both firms play their respective equilibrium strategies for the corresponding competition level. As discussed previously, these are: 
\begin{itemize}
\item \DG in the monopoly, 
\item \DG for both firms in duopoly (Finding \ref{find:duopoly}),
\item \TS for the incumbent (Finding \ref{find:temp-monopoly}) and \DG for the entrant in temporary monopoly (Finding \ref{find:temp-monopoly-entrant}).
\end{itemize}
} %%%%%%%

Figure \ref{eq_regret} displays the market regret (averaged
  over multiple runs) under different levels of competition.
Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. \asedit{Recall that under temporary monopoly, the incumbent is incentivized to play \TS. Moreover, we find that the welfare is close to that of having a single firm for all agents and running \TS. We also observe that monopoly and duopoly achieve similar welfare.}
%with monopoly being marginally better than duopoly.

@@

\asedit{Finding~\ref{find:welfare}(b) is interesting because, in equilibrium, both firms play \DG in both settings, and one might conjecture that the welfare should increase with the number of firms playing \DG. Indeed, one run of \DG may get stuck on a bad arm. However, two firms independently playing \DG are less likely to get stuck simultaneously. If one firm gets stuck and the other does not, then the latter should attract most agents, leading to improved welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and \Eeog as we increase \#firms playing \DG}
\label{many_firm_welfare}
\end{figure}

@@

\asedit{We track the average \Eeog in each of the
simulations and notice that it \textit{increases} with the number of firms.
This observation also runs counter of the intuition that with more firms running \DG, one of them is more likely to ``get lucky" and take over the market (which would cause \Eeog to \emph{decrease} with the number of firms).}

>>>>

\xhdr{Welfare implications.}
We study the effects of competition on consumer welfare: the total reward collected by the users over time. Rather than welfare directly, we find it more lucid to consider
\emph{market regret}:
\[ \textstyle T\, \max_a \mu(a) - \sum_{t\in [T]} \mu(a_t), \]
where $a_t$ is the arm chosen by agent $t$. This is a standard performance measure in the literature on multi-armed bandits. Note that smaller regret means higher welfare.

@@

We assume that both firms play their respective equilibrium strategies for the corresponding competition level. As discussed previously, these are:
\begin{itemize}
\item \DG in the monopoly,
\item \DG for both firms in duopoly (Finding \ref{find:duopoly}),
\item \TS for the incumbent (Finding \ref{find:temp-monopoly}) and \DG for the entrant in temporary monopoly (Finding \ref{find:temp-monopoly-entrant}).
\end{itemize}

Figure \ref{eq_regret} displays the market regret (averaged
  over multiple runs) under different levels of competition.
Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. Recall that under temporary monopoly, the incumbent is incentivized to play \TS. Moreover, we find that the welfare is close to that of having a single firm for all agents and running \TS. We also observe that monopoly and duopoly achieve similar welfare.
%with monopoly being marginally better than duopoly.

@@

Finding~\ref{find:welfare}(b) is interesting because, in equilibrium, both firms play \DG in both settings, and one might conjecture that the welfare should increase with the number of firms playing \DG. Indeed, one run of \DG may get stuck on a bad arm. However, two firms independently playing \DG are less likely to get stuck simultaneously. If one firm gets stuck and the other does not, then the latter should attract most agents, leading to improved welfare.
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and \Eeog as we increase \#firms playing \DG}
\label{many_firm_welfare}
\end{figure}

@@

We track the average \Eeog in each of the
simulations and notice that it \textit{increases} with the number of firms.
This observation also runs counter of the intuition that with more firms running \DG, one of them is more likely to ``get lucky" and take over the market (which would cause \Eeog to \emph{decrease} with the number of firms).
